Model-View-Controller Package

### 2005-12-13 inst/doc/MVCClass.Rnw
Changed the vignette to incorporate the new classes.
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MVCClass@15363 bc3139a8-67e5-0310-9ffc-ced21a209358

The model class is responsible for storing and updating the data.  These two
functions are reflected in Figure \ref{Fig:Model}, which shows the inheritance
structure for the model classes.  Here the virtual class,
\Robject{gModel}, has the slots modelData, linkData, virtualData, and
modelName.  These four slots are common information that all models will
need.  The modelData slot is the data set for this model, the linkData slot is
a list of two functions, \Rfunction{linkToParent} and \Rfunction{linkToChild},
which link this model to its parent and child models, respectively (see Section
\ref{Sec:MVC}), the virtualData slot is data pertaining to the views
that needs to be stored with the model so that it can be shown in all views of
this model, and the modelName slot is the name of the model.

@@

\begin{figure}[ht]
  \begin{center}
    \scalebox{0.7}{\includegraphics{VigMessageClass2.jpg}}
    \caption{ Inheritance for Message Classes that are Passed Between MVCs. }
    \label{Fig:BetwMess}
  \end{center}
\end{figure}

@@

The next two message classes pertain to updating MVC objects when a parent MVC
or child MVC object has changed.  These classes are
\Robject{gUpdateParentMessage} and \Robject{gUpdateChildMessage} and they both
inherit from the \Robject{gMessage} class, as shown in Figure
\ref{Fig:BetwMess}.  Even though they are both update messages, they do not
inherit from the \Robject{gUpdateMessage} class because the information they
need to contain is a \Robject{gUpdateDataMessage} object.  Thus, the
\Robject{gUpdateParentMessage} class has one slot, childUpdateDataMessage, and
this slot contains the \Robject{gUpdateDataMessage} object that was used to
update the child model.  Similarly, the \Robject{gUpdateChildMessage} class
has two slots, parentUpdateDataMessage and childName, where the
parentUpdateDataMessage slot contains the \Robject{gUpdateDataMessage} object
that was used to update the parent model and the childName slot contains the
name of the child model that is being updated (because a parent MVC can have
more than one child MVC).

>>>>

The model class is responsible for storing and updating the data.  These two
functions are reflected in Figure \ref{Fig:Model}, which shows the inheritance
structure for the model classes.  Here the virtual class,
\Robject{gModel}, has the slots modelData, linkData, virtualData, and
modelName.  These four slots are common information that all models will
need.  The modelData slot is the data set for this model, the linkData slot is
a list of two functions, \Rfunction{toParent} and \Rfunction{fromParent},
which link this model to its parent and child models, respectively (see Section
\ref{Sec:MVC}), the virtualData slot is data pertaining to the views
that needs to be stored with the model so that it can be shown in all views of
this model, and the modelName slot is the name of the model.

@@

\begin{figure}[ht]
  \begin{center}
    \scalebox{0.7}{\includegraphics{newVigMessageClass2.jpg}}
    \caption{ Inheritance for Message Classes that are Passed Between MVCs. }
    \label{Fig:BetwMess}
  \end{center}
\end{figure}

@@

The next two message classes pertain to updating MVC objects when a parent MVC
or child MVC object has changed.  These classes are
\Robject{gSendParentMessage} and \Robject{gSendChildMessage} and they both
inherit from the \Robject{gMessage} class, as shown in Figure
\ref{Fig:BetwMess}.  The information these two classes
need to contain is a \Robject{gUpdateDataMessage} object.  Thus, the
\Robject{gSendParentMessage} class has one slot, childUpdateDataMessage, and
this slot contains the \Robject{gUpdateDataMessage} object that was used to
update the child model.  Similarly, the \Robject{gSendChildMessage} class
has two slots, parentUpdateDataMessage and childName, where the
parentUpdateDataMessage slot contains the \Robject{gUpdateDataMessage} object
that was used to update the parent model and the childName slot contains the
name of the child model that is being updated (because a parent MVC can have
more than one child MVC).
